---
title: "Practical_Machine_Learning_Project"
author: ""
date: "September 21, 2014"
output: html_document
---
#Getting and Cleaning Data
Download the training and testing data sets and remove the columns with non-related infomation and invalid columns with more than 95% missing values.

```{r}
library(caret)
#download data sets
train<-read.csv("./train.csv")
test<-read.csv("./test.csv")
#remove non-related columns
training <- train[,7:dim(train)[2]]
testing <- test[,7:dim(test)[2]]
##remove invalid columns with more than 95% missing values, learned from http://mlarocca.github.io/07-23-2014/analysis.html
threshold <- dim(train)[1]*0.95
goodColumns <- !apply(training, 2, function(x) sum(is.na(x)) > threshold  || sum(x=="") > threshold)
training <- training[,goodColumns]

badColumns <- nearZeroVar(training, saveMetrics = TRUE)
training <- training[, badColumns$nzv==FALSE]
```

#Data Slicing and Cross Validation 
Assign data rows into training set and crossv alication set

```{r}
inTrain <- createDataPartition(training$classe, p = 0.7)[[1]]
cv_train <- training[inTrain,]
cv_test <- training[-inTrain,]

inTrain <- createDataPartition(cv_test$classe, p = 0.7)[[1]]
cv_training <- cv_train[inTrain,]
cv_testing <- cv_test[inTrain,]

testing <- testing[, goodColumns]
testing$classe <- NA
testing <- testing[, badColumns$nzv==FALSE]
```

#Model Training
Training models using method "rf", "gbm" and "lda". Give up method "rf" here because the performance is not good in this case.

```{r}
##Train 3 different models
#mod1 <- train(classe ~ ., data=cv_train, method="rf")
mod2 <- train(classe ~ ., data=cv_train, method="gbm")
mod3 <- train(classe ~ ., data=cv_train, method="lda")

#pred1 <- predict(mod1, cv_test)
pred2 <- predict(mod2, cv_test)
pred3 <- predict(mod3, cv_test)

#confusionMatrix(pred1, crossv$classe)
confusionMatrix(pred2, crossv$classe)
confusionMatrix(pred3, crossv$classe)

predDF <- data.frame(pred2, pred3, classe=cv_train$classe)

combModFit <- train(classe ~ ., method="rf", data=predDF)
```

#Prediction error

```{r}
#in-sample error
combPredIn <- predict(combModFit, predDF)
confusionMatrix(combPredIn, predDF$classe)

#out-of-sample error
#pred1 <- predict(mod1, cv_testing)
pred2 <- predict(mod2, cv_testing)
pred3 <- predict(mod3, cv_testing)
predDF <- data.frame(pred1,pred2, pred3, classe=cv_testing$classe)

combPredOut <- predict(combModFit, predDF)
confusionMatrix(combPredOut, predDF$classe)
```

#Write the Prediction Results
```{r}
pml_write_files = function(x){
        n = length(x)
        for(i in 1:n){
                filename = paste0("problem_id_",i,".txt")
                write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
        }
}

pml_write_files(combPred)
```
